---
output: github_document
title: ""
author: ""
date: ""
---
```{r,echo=FALSE}
knitr::opts_chunk$set(comment='.', message=FALSE, 
                      fig.path="inst/maintenance/img/README-")
```



# mrgsolvetk
A toolkit to be used with `mrgsolve`


# Examples
```{r}
library(ggplot2)
library(dplyr)
library(mrgsolve)
library(mrgsolvetk)

mod <- mread_cache("pk1cmt",modlib())

mod <- ev(mod, amt=100) %>% Req(CP) %>% update(end = 48, delta = 0.25)

param(mod)
```



## Sensitivity analyses

### `sens_unif`

- Draw parameters from uniform distribution based on current parameter values
- `lower` and `upper` scale the parameter value to provide `a` and `b` arguments to `runif`

```{r}
out <- 
  mod %>% 
  select(CL,VC,KA1) %>%
  sens_unif(.n=10, lower=0.2, upper=3)

out

sens_plot(out, CP)
```


We can also make a univariate version of this

```{r}

mod %>% 
  select(CL,VC,KA1) %>%
  sens_unif(.n=10, lower=0.2, upper=3, univariate = TRUE) %>%
  sens_plot(CP, split = TRUE)
```


### `sens_norm`

- Draw parameters from (log) normal distribution based on current parameter 
values and `%CV`

```{r}
mod %>% 
  select(CL,VC) %>%
  sens_norm(.n=10, cv=30) %>%
  sens_plot(CP)
```

### `sens_seq`

- Give a sequence for one or more parameters

```{r}
mod %>% sens_seq(CL = seq(2,12,2), VC = seq(30,100,10)) %>% sens_plot(CP)
```


### `sens_range`

- Create sets of parameters equally-spaced between two bounds

```{r}
mod %>%
  select(CL,VC) %>%
  sens_range(.n = 5, .factor = 4) %>%
  sens_plot(CP, split = TRUE)
```

or

```{r}

mod %>%
  sens_range(CL = c(0.5, 1.5), VC = c(10,40), .n = 5) %>%
  sens_plot(CP)
```



### `sens_grid`

- Like `sens_seq` but performs all combinations

```{r}
mod %>%  sens_grid(CL = seq(1,10,1), VC = seq(20,40,5)) %>% sens_plot(CP)
```

### `sens_covset`

- Use `dmutate` to generate random variates for each parameter 

```{r}
cov1 <- dmutate::covset(CL ~ runif(1,3.5), VC[0,] ~ rnorm(50,25))

cov1
```

```{r}
out <- mod %>% sens_covset(cov1) 
```

```{r}
out

distinct(out,ID,CL,VC)

```


`
