---
output:
  md_document:
    variant: markdown_github
title: ""
author: ""
date: ""
---
```{r,echo=FALSE}
knitr::opts_chunk$set(comment='.', message=FALSE)
```



# mrgsolvetk
A toolkit to be used with `mrgsolve`


# Examples
```{r}
library(dplyr)
library(mrgsolve)
library(mrgsolvetk)

mod <- mread_cache("pk1cmt",modlib())
mod <- ev(mod, amt=100) %>% Req(CP)

param(mod)
```



## Sensitivity analyses

### `sens_unif`

- Draw parameters from uniform distribution based on current parameter values
- `lower` and `upper` scale the parameter value to provide `a` and `b` arguments to `runif`

```{r}
mod %>% sens_unif(n=10, pars="CL,VC,KA1", lower=0.2, upper=3)
  
```

### `sens_norm`

- Draw parameters from (log) normal distribution based on current parameter values and `%CV`

```{r}
mod %>% sens_norm(n=10, pars="CL,VC", cv=30)
```

### `sens_seq`

- Give a sequence for one or more parameters

```{r}
mod %>% sens_seq(CL = seq(2,12,2), VC = seq(30,100,10))
```


### `sens_grid`

- Like `sens_seq` but performs all combinations

```{r}
mod %>%  sens_grid(CL = seq(1,10,1), VC = seq(20,40,5))
```

### `sens_covset`

- Use `dmutate` to generate random variates for each parameter 

```{r}
cov1 <- dmutate::covset(CL ~ runif(1,3.5), VC[0,] ~ rnorm(50,25))

cov1
```

```{r}
out <- mod %>% sens_covset(cov1) 
```

```{r}
out

distinct(out,ID,CL,VC)
```



# Estimation `stats::optim`

## Load a data set
```{r}
data(exTheoph)
df <- mutate(exTheoph, DV = conc)
```


## Load a model
```{r}
mod <- mread("pk1cmt", modlib())
```

## Define an objective function
```{r}
ofv <- function(dv,pred,par) -1*sum(dnorm(dv,pred,par$sigma,log=TRUE))
```


## Define parameters to estimate
```{r}
library(optimhelp)
par <- parset(log_par("CL", 0.1),
              log_par("VC", 1.1),
              log_par("KA1",1.1),
              log_par("sigma",1))
```



## Fit 
- `ID==3`
```{r}
fit <- 
  mod %>% 
  data_set(df, ID==3) %>%
  fit_optim(pred="CP",ofv=ofv,par=par)
```

```{r}
fit$pars
```


## Plot

```{r,fig.path="inst/maintenance/img/README-"}
library(ggplot2)
ggplot(data=fit$tab) + 
  geom_point(aes(time,conc)) +
  geom_line(aes(time,PRED)) 
```


## With fixed parameter
```{r}
library(optimhelp)
par <- parset(log_par("CL", 0.1),
              log_par("VC", 1.1),
              log_par("KA1",1.9,fixed=TRUE),
              log_par("sigma",1))
```



## Fit
```{r}
fitt <- 
  mod %>% 
  data_set(df, ID==3) %>%
  fit_optim(pred="CP",ofv=ofv,par=par)
```

```{r}
fitt$pars
fit$value
fitt$value

```
